%\divider
\cvsection{Projects}
\cvproject{\href{https://kliinik.logopeed.ee}{kliinik.logopeed.ee}}
\begin{itemize}
\item Successfully developed a system for speech therapists and their patients to enhance the therapy process. I was responsible for managing the full life cycle of the project including gathering requirements, creating mock-ups, implementing the app, and deploying it to the data center. These efforts resulted in a user-friendly, efficient tool that improved the therapy experience for both therapists and patients, leading to better outcomes and satisfaction for all parties involved.
\end{itemize}
\smallskip
\smallskip
\cvproject{\href{https://event.logopeed.ee}{event.logopeed.ee}}
\begin{itemize}
\item Successfully designed and developed a WordPress site for managing a yearly speech therapist conference, including tasks such as setting up the site structure, designing the layout and visual elements, and configuring the necessary plugins and features. These efforts resulted in a user-friendly, organized platform for managing conference logistics and communication, improving the efficiency and effectiveness of the conference for both organizers and attendees.
\end{itemize}
\cvproject{\href{https://medlife.ee}{medlife.ee}}
\begin{itemize}
\item Designed and developed a custom WordPress theme from the ground up for a healthcare news outlet, gaining valuable expertise in both WordPress internals and project management skills in the process.
\end{itemize}
\cvproject{\href{https://www.nooredolumpiale.ee/}{Pro bono - Noored Olümpiale}}
\begin{itemize}
\item (Not the current site) Developed the user interface for a website on top of Voog CMS for a fundraising campaign to support promising young Estonian athletes. Website design was created by design agency Velvet.
\end{itemize}


% \cvachievement{\faTrophy}{}{Received accolades at Atos for Best Performance in team.}
% \cvachievement{\faTrophy}{}{Received Best Debut Award at Atos. }
% %\divider
% \cvachievement{\faInstitution}{}{Won 2nd Consolation Prize for paper presented on Cognitive Radio Networks.}
% %\divider
% \cvachievement{\faGraduationCap}{}{Got Selected in "Exclusive Scholar Program" during undergrad.}
% %\divider
% \cvachievement{\faDollar}{}{Awarded with Narotam Sekhsaria Foundation Scholarship}
%\cvsection{Strengths}

%\cvtag{Hard-working (18/24)} 
%\cvtag{Persuasive}
%\cvtag{Motivator \& Leader}

%\divider\smallskip

%\cvtag{UX}
%\cvtag{Mobile Devices \& Applications}
%\cvtag{Product Management \& Marketing}


%\divider

%\cvevent{B.S.\ in Symbolic Systems}{Stanford University}{Sept 1993 -- June 1997}{}

\cvsection{Technical skills}
\smallskip
\begin{itemize}
\item \textbf{Backend} - Scala, TypeScript, Python, C\#
\smallskip
\item \textbf{Frontend} - TypeScript, SCSS \& BEM, React
\smallskip
\end{itemize}

\cvsection{Soft skills}
\smallskip
\begin{itemize}
\item Team player
\smallskip
\item Ability to work under pressure
\smallskip
\item Comfortable Working Independently
\smallskip
\item Ability to take initiative to solve problems
\end{itemize}

\cvsection{Hobbies}
\smallskip
\begin{itemize}
\item Football, racket sports, crossfit
\smallskip
\item Automating the boring stuff
\smallskip
\item Investing
\end{itemize}