\documentclass[10pt,a4paper,ragged2e]{altacv}
\geometry{left=2cm,right=10cm,marginparwidth=6.8cm,marginparsep=1.2cm,top=1.25cm,bottom=1.25cm}
\ifxetexorluatex
  \setmainfont{Carlito}
\else
  \usepackage[utf8]{inputenc}
  \usepackage[T1]{fontenc}
  \usepackage[default]{lato}
\fi
\usepackage{hyperref}
\definecolor{VividPurple}{HTML}{000000}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{2E2E2E}
\colorlet{heading}{VividPurple}
\colorlet{accent}{VividPurple}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}
\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}
\addbibresource{sample.bib}

\begin{document}
\name{Tristan Krass}
\tagline {I am a software engineer dedicated to building user-friendly products that create value for people. I am committed to continuous learning in order to constantly improve my skills and the products I build.}
\personalinfo{%
  % Not all of these are required!
  % You can add your own with \printinfo{symbol}{detail}
  \email{tristankrass@gmail.com}
%   \phone{000-00-0000}
%  \mailaddress{Address, Street, 00000 County}
  % \location{Tallinn, Estonia}
  \githubsymbol{\href{https://github.com/tristankrass}{tristankrass}}
  \homepage{\href{https://tristan.ee}{tristan.ee}}
%  \twitter{@marissamayer}
  \linkedin{\href{https://www.linkedin.com/in/tristankrass/}{tristankrass}}
%   \orcid{orcid.org/0000-0000-0000-0000} % Obviously making this up too. If you want to use this field (and also other academicons symbols), add "academicons" option to \documentclass{altacv}
}

%% Make the header extend all the way to the right, if you want.
\begin{fullwidth}
\makecvheader
\end{fullwidth}

%% Depending on your tastes, you may want to make fonts of itemize environments slightly smaller
\AtBeginEnvironment{itemize}{\small}

%% Provide the file name containing the sidebar contents as an optional parameter to \cvsection.
%% You can always just use \marginpar{...} if you do
%% not need to align the top of the contents to any
%% \cvsection title in the "main" bar.
\cvsection[page1sidebar]{Experience}

\cvevent{}{Twilio - Software Engineer}{(Internship 2020 Summer), full time June 2021 - }{}
\begin{itemize}
\item Working on real time monitoring system for detecting network anomalies. Creating and maintaining systems that processed up to 55 thousand records a minute during the peak times.
\smallskip
\item Building internal tooling for operations. Collaborated closely with stakeholders and product manager to identify the most effective solution after thorough analysis and consideration of multiple options.
\smallskip
\item Successfully improved and maintained legacy systems, including a small rewrite of one system that resulted in significant cost savings.
\smallskip
\item Onboarding and training new engineers in tech, tools and process on our team.
\smallskip
\item Main technologies used - Scala, Spark, Akka, ZIO, TypeScript and React.
\end{itemize}

\divider

\cvevent{}{Alvin.ai - Software Engineer}{Summer, 2019}{}
\begin{itemize}
\item As the first engineer at the startup (besides the founders), I played a critical role in working closely with the founders to identify the product-market fit and guide the company's technical direction. Despite operating under a tight schedule, I effectively contributed to the company's early success.
\smallskip
\item In close collaboration with the CTO, I played a key role in developing the MVP for the company. Specifically, I focused on building the SQL editor and the web platform for data analysts.
\smallskip
\item Main technologies used - TypeScript, React, NestJS, Firebase and GCP.
\end{itemize}

\divider

\cvevent{}{Freelancing}{}{}
\begin{itemize}
\item Successfully led the full life cycle of multiple software development projects, including gathering requirements, building projects from start to finish independently, setting up CI/CD pipelines, managing servers, and effectively communicating with clients. These efforts resulted in high-quality, reliable software solutions that met the needs and expectations of clients.
\end{itemize}


\cvsection{Education}
\cvevent{}{Tallinn University of Technology - IT Systems Development | Cum laude}{ 2018-2021}{}
\begin{itemize}
\item Served as a teaching assistant for a programming course in Python.
\smallskip
\item \href{https://www.geeksonwheels.eu/}{Geeks on Wheels} programming lab coordinator.
\end{itemize}
\cvevent{}{Old Town Educational College - Division of Math and Sciences}{ 2005 - 2017 }{}


% \cvevent{Product Engineer}{Google}{23 June 1999 -- 2001}{Palo Alto, CA}

% \begin{itemize}
% \item Joined the company as employe \#20 and female employee \#1
% \item Developed targeted advertisement in order to use user's search queries and show them related ads
% \end{itemize}

%\cvsection{A Day of My Life}

% Adapted from @Jake's answer from http://tex.stackexchange.com/a/82729/226
% \wheelchart{outer radius}{inner radius}{
% comma-separated list of value/text width/color/detail}
% Some ad-hoc tweaking to adjust the labels so that they don't overlap
% \wheelchart{1.5cm}{0.5cm}{%
%   10/10em/accent!30/Sleeping \& dreaming about work,
%   25/9em/accent!60/Public resolving issues with Yahoo!\ investors,
%   5/13em/accent!10/\footnotesize\\[1ex]New York \& San Francisco Ballet Jawbone board member,
%   20/15em/accent!40/Spending time with family,
%   5/8em/accent!20/\footnotesize Business development for Yahoo!\ after the Verizon acquisition,
%   30/9em/accent/Showing Yahoo!\ employees that their work has meaning,
%   5/8em/accent!20/Baking cupcakes
% }

\clearpage

% \cvsection[page2sidebar]{Publications}

\nocite{*}

% \printbibliography[heading=pubtype,title={\printinfo{\faBook}{Books}},type=book]

% \divider

% \printbibliography[heading=pubtype,title={\printinfo{\faFileTextO}{Journal Articles}}, type=article]

% \divider

% \printbibliography[heading=pubtype,title={\printinfo{\faGroup}{Conference Proceedings}},type=inproceedings]

% %% If the NEXT page doesn't start with a \cvsection but you'd
% %% still like to add a sidebar, then use this command on THIS
% %% page to add it. The optional argument lets you pull up the
% %% sidebar a bit so that it looks aligned with the top of the
% %% main column.
% % \addnextpagesidebar[-1ex]{page3sidebar}


\end{document}
